### 2017-01-09 thesis/latex/thesis.tex
Add work to methods. Doesn't compile. Todo: make compile and finish methods.

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins

\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

@@

\section{Chapter: Methods}
\subsection{Simulation}
Talk about why simulation is the only way to verify the mechanochemical cycle, since experiments
aren't high resolution enough to make good videos of the walk, and even if they were, in some sense
knowing that dynein behaves identically to a simple mathematical model is more informative than
a video, since there is lots of information in a video and really precise info in a simulation.\\

@@

\subsection{Simulating our model}
Talk generally about what simulating stuff means.\\
\subsubsection{Motion equations}

\paragraph{a Onebound solution}
Discuss how our model is represented by the following figure (maybe get one with springs on the
hinges):\\

\begin{figure}
  \centering
  \includegraphics[width=.45\textwidth]{../figures/equilibrium-onebound}
  \caption{Definition of equilibrium angles.}
  \label{fig:eq_angles}
\end{figure}

Show the derivation process.\\

\paragraph{b Bothbound solution}
Show how bothbound is derived and different from onebound. Put the actual equations in the appendix,
or just leave them out 'cause they're ugly?\\

\subsubsection{Code}
Talk about using C++, Make, C, Python. Talk about the rough program flow, how we go from code to
data.\\

\paragraph{a Running, compiling, language choice?}
Details on why we chose C++.\\
\subsubsection{Time evolution}
How we do time evolution.
\paragraph{Euler’s method}
Show how Euler's method is arrived at, how its error scales, why we use it.

@@

\paragraph{Finding the right dt}
Figure on error rate vs. dt.

\paragraph{State transitions}
Talk about how we calculate transition rates based on differences in energies between states.
Then how we use transition rates to transition our model accurately.\\

@@

\subsection{Verifying our model}
Talk about why we think our model accurately represents the system we are trying to model, and
doesn't have bugs in it.\\

Talk about this figure:

@@

and how it shows our model is physical, or at least, how obeying the equipartition theorem shows
how our domains both feel harmonic energies and can fully explore their spaces?\\

\subsection{Parameters}
The following table shows our guess parameters from various papers/crystal structures.\\

                        \begin{center}
  \begin{tabular}{| l | l | l | l | l | l |}
    \hline
    & Winch (Sarlah) & Schmidt & Lin & PyMol 3VKH & PyMol 4RH7\\\hline
    $L_s$ & 12nm & & & 21.0nm & 22.1nm\\ \hline
    $L_t$ &  7nm & & & & 11.15nm\\ \hline
    $R_b$ &  & & & 1.57nm & 1.45nm\\ \hline
    $R_m$ &  7nm & & & 7.36nm & 6.3nm\\ \hline
    $R_t$ &  & & & & 2.16nm \\ \hline
    $\theta_{m}^{Pre}$ & 250$^{\circ}$ & & 171$^{\circ}$ & &\\ \hline
    $\theta_{m}^{Post}$ & 330$^{\circ}$ & & 137.5$^{\circ}$ & &\\ \hline
    $\theta_{b}$ & 56$^{\circ}$ & & 63.5$^{\circ}$ & &\\ \hline
    $\theta_{t}$ & 0$^{\circ}$ & & & &\\ \hline
    $k_{ub}$ & $180 s^{-1,a}$ & & & &\\ \hline
    $k_b$ & $5000 s^{-1,b}$ & & & &\\ \hline
  \end{tabular}
\end{center}
		\subsubsection{Lengths, angles, binding constants, etc…}
	\subsection{Tuning our model}
	\subsubsection{Searching for optimal parameters}
\section{Chapter: Results}
	\subsection{Histograms}
		\subsubsection{Step length histograms}
		\subsubsection{Step time histograms}
	\subsection{Other ways to represent data?}

@@

>>>>

\usepackage[hmargin=1.25cm, vmargin=1.5cm]{geometry} % Document margins
\usepackage[usenames,dvipsnames]{xcolor} % Allows the definition of hex colors

\usepackage{listings}
\lstset{escapechar=\&}

@@

\subsection{Simulation}
Talk about why simulation is the only way to verify the mechanochemical cycle, since experiments
aren't high resolution enough to make good videos of the walk, and even if they were, in some sense
knowing that dynein behaves identically to a simple mathematical model is more informative than
a video, since there is lots of information in a video and really precise info in a simulation.\\

@@

\paragraph{Euler’s method}
Show how Euler's method is arrived at, how its error scales, why we use it.

@@

@@

\section{Chapter: Methods}

\subsection{Dynein Models}
In order to simulate a protein's passage through the above mechanochemical cycle, two mathematical models are needed: one for the prestroke, MTBD-detached state, and one for the poststroke, MTBD-bound state. The purpose of each model is to calculate the position and velocity of each domain at an arbitrary time.\\

\subsubsection{Prestroke onebound model}
Prestroke dynein is referred to as onebound, since one motor domain is bound to the MT in this state, and the other unbound. A spatial representation of onebound dynein is shown in Figure \ref{ob_fig}.

\begin{figure}[h]
  \centering
  \includegraphics[width=.45\textwidth]{../figures/ob_fig.pdf}
  \caption{Definition of equilibrium angles.}
  \label{ob_fig}
\end{figure}

TODO: label domain names (MTBD motor tail), Ls, Lt, microtubule\\

Each domain is represented by a point, and is connected to other domains via fixed-length rods. Angles represent the degrees of freedom of the model. Since the protein is a dimer, there are two copies of the MTB, motor and tail domains. The tails are fused together and so represented as a single point. The motor and MTB domains are given a ``bound'' and ``unbound'' designation to differentiate them. The ``bound'' domains are the MTBD attached to the MT and its corresponding motor domain. The unbound domains are the unbound MTBD and its corresponding motor domain.\\

\paragraph{Angular and Cartesian coordinates}

The four angles $\Theta_{bb}, \Theta_{bm}, \Theta_{um}$ and $\Theta_{ub}$, corresponding to bound binding, bound motor, unbound motor and unbound binding angle, together describe any possible conformation the system can take on. The domain of $\Theta_{bb}$ has a restricted domain of $[0,\pi]$ to prevent below-MT conformations, but the other angles have domains of $[0,2\pi]$. Each angle is defined relative to the horizontal axis.\\

\begin{figure}[h]
  \centering
  \begin{tabular}{c}
    \begin{lstlisting}[language=C++]
      class Dynein_onebound{
        double &$\Theta_{bb}, \Theta_{bb}, \Theta_{bb}, \Theta_{bb}$&
        double &$\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$&
        double &$X_{bb}$&
      }
    \end{lstlisting}
  \end{tabular}
  \caption{Pseudocode of the onebound Dynein model.}
  \label{ob_struct}
\end{figure}

Pseudocode for the numerical onebound model representation is shown in Figure \ref{ob_struct}. The position of the bound binding domain $X_{bb}$ and the four domain angles are all the values needed to determine the position of the protein at any time. The following equations allow recursive calculation of the positions of each domain in cartesian coordinates:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  X_{bm} &= X_{bb}+L_{s}\cos(\Theta_{bb}) \\
  X_{t}  &= X_{bm}+L_{t}\cos(\Theta_{bm}) \\
  X_{fm} &= X_{t} - L_{t}\cos(\Theta_{fm}) \\
  X_{fb} &= X_{fm} - L_{s}\cos(\Theta_{fb})
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}
  Y_{bb} &= 0 \\
  Y_{bm} &= Y_{bb}+L_{s}\sin(\Theta_{bb}) \\
  Y_{t}  &= Y_{bm}+L_{t}\sin(\Theta_{bm}) \\
  Y_{fm} &= Y_{t} - L_{t}\sin(\Theta_{fm}) \\
  Y_{fb} &= Y_{fm} - L_{s}\sin(\Theta_{fb})
\end{align}
\end{minipage}
\vspace{.5cm}

$L_s$ and $L_t$ correspond to lengths of each interdomain rod, and the $t$ subscripts refer to tail domain coordinates.\\

\paragraph{Angular and Cartesian velocities}
The goal is to express angular velocities $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ in terms of known quantities. To begin, the cartesian velocities of each domain can be calculated from the above position equations in a similar recursive manner:

\noindent\begin{minipage}{0.49\linewidth}
\begin{align}
  \dot{X}_{bb} &= 0 \\
  \dot{X}_{bm} &= \dot{X}_{bb} - L_{s}\sin(\Theta_{bb})\dot{\Theta}_{bb} \label{cartesian-bmx}\\
  \dot{X}_{t } &= \dot{X}_{bm} - L_{t}\sin(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{X}_{fm} &= \dot{X}_{t } + L_{t}\sin(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{X}_{fb} &= \dot{X}_{fm} + L_{s}\sin(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\begin{minipage}{0.49\linewidth}
\begin{align}                                                                          
  \dot{Y}_{bb} &= 0 \\                                                        
  \dot{Y}_{bm} &= \dot{Y}_{bb} + L_{s}\cos(\Theta_{bb})\dot{\Theta}_{bb} \\
  \dot{Y}_{t}  &= \dot{Y}_{bm} + L_{t}\cos(\Theta_{bm})\dot{\Theta}_{bm} \\
  \dot{Y}_{fm} &= \dot{Y}_{t } - L_{t}\cos(\Theta_{fm})\dot{\Theta}_{fm} \\
  \dot{Y}_{fb} &= \dot{Y}_{fm} - L_{s}\cos(\Theta_{fb})\dot{\Theta}_{fb}
\end{align}
\end{minipage}
\vspace{.5cm}

Another way to express these cartesian velocities is using the Brownian dynamics equation $\dot{X} = \frac1\gamma F_{net} + R$:

\begin{align}  
  \dot{X}_{bm} &= \frac{1}{\gamma_m} \Big(F_{xml} + - \lambda_{bs}(X_{bm} - X_{bb}) + \lambda_{bt}(X_{t } - X_{bm}) \Big) + R_{xml} \label{brownian-bmx}\\
  \dot{X}_{t } &= \frac{1}{\gamma_t} \Big(F_{xt } + - \lambda_{bt}(X_{t } - X_{bm}) + \lambda_{ft}(X_{fm} - X_{t }) \Big) + R_{xt } \\
  \dot{X}_{fm} &= \frac{1}{\gamma_m} \Big(F_{xmr} + - \lambda_{ft}(X_{fm} - X_{t }) + \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xmr} \\
  \dot{X}_{fb} &= \frac{1}{\gamma_b} \Big(F_{xbr} + - \lambda_{fs}(X_{fb} - X_{fm}) \Big) + R_{xbr}
\end{align}

\begin{align}  
  \dot{Y}_{bm} &= \frac{1}{\gamma_m} \Big(F_{yml} + - \lambda_{bs}(Y_{bm} - Y_{bb}) + \lambda_{bt}(Y_{t } - Y_{bm}) \Big) + R_{yml} \\
  \dot{Y}_{t}  &= \frac{1}{\gamma_t} \Big(F_{yt } + - \lambda_{bt}(Y_{t } - Y_{bm}) + \lambda_{ft}(Y_{fm} - Y_{t }) \Big) + R_{yt } \\
  \dot{Y}_{fm} &= \frac{1}{\gamma_m} \Big(F_{ymr} + - \lambda_{ft}(Y_{fm} - Y_{t }) + \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ymr} \\
  \dot{Y}_{fb} &= \frac{1}{\gamma_b} \Big(F_{ybr} + - \lambda_{fs}(Y_{fb} - Y_{fm}) \Big) + R_{ybr}
\end{align}

where $\gamma_n$ is a drag coefficient for the binding, motor or tail domain with units of mass per second. $F_{xn}$ is the x component of external force on each domain $n$ due to various factors. $\lambda_{12}\left(X_1 - X_2\right)$ is the x component of internal force on domain $2$ due to domain $1$, where $\lambda$ is a tension coefficient with units of mass per second per second. $R_{xn}$ is the Brownian coefficient representing motion due to solvent collision, with units of velocity.\\

These two sets of equations, cartesian and Brownian, can be equated to get more interesting equations. For example, Eq (\ref{cartesian-bmx}) and Eq (\ref{brownian-bmx}) can be equated. This equating, combined with expanding the recursive velocity definitions leads to:

\begin{align*}
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} &= \frac{1}{\gamma_m}F_{xml} + -\frac{1}{\gamma_m}\lambda_{bs}(X_{bm} - X_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(X_{t } - X_{bm}) + R_{bmx} \\
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{xt } + -\frac{1}{\gamma_t}\lambda_{bt}(X_{t } - X_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(X_{um} - X_{t }) + R_{tx} \\
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{xmr} + -\frac{1}{\gamma_m}\lambda_{ft}(X_{um} - X_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(X_{ub} - X_{um}) + R_{bmx} \\
  -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{xbr} + -\frac{1}{\gamma_b}\lambda_{fs}(X_{ub} - X_{um}) + R_{bbx}
\end{align*}

\begin{align*}
  L_s\cos(\theta_{bb})\dot{\theta}_{bm} &= \frac{1}{\gamma_m}F_{yml} + -\frac{1}{\gamma_m}\lambda_{bs}(Y_{bm} - Y_{bb}) + \frac{1}{\gamma_m}\lambda_{bt}(Y_{t } - Y_{bm}) + R_{umy} \\
  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} &= \frac{1}{\gamma_t}F_{yt } + -\frac{1}{\gamma_t}\lambda_{bt}(Y_{t } - Y_{bm}) + \frac{1}{\gamma_t}\lambda_{ft}(Y_{um} - Y_{t }) + R_{ty} \\
  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} &= \frac{1}{\gamma_m}F_{ymr} + -\frac{1}{\gamma_m}\lambda_{ft}(Y_{um} - Y_{t }) + \frac{1}{\gamma_m}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bmy} \\
  L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub} &= \frac{1}{\gamma_b}F_{ybr} + -\frac{1}{\gamma_b}\lambda_{fs}(Y_{ub} - Y_{um}) + R_{bby}
\end{align*}

These eight equations form a system of equations with eight unknowns: $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$, and the four tension coefficients $\lambda_{bs}, \lambda_{bt}, \lambda_{um}$ and $\lambda_{ub}$. This system is more compactly represented as:
{\small
  \[
  \hspace{-1.0cm}
  \resizebox{0.85\linewidth}{!}{%
  $\begin{pmatrix}
    L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gamma_m (X_{bm} - X_{bb}) & \gamma_m (X_{t } - X_{bm}) & 0 & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (X_{t } - X_{bm}) & \gamma_t (X_{um} - X_{t }) & 0\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (X_{um} - X_{t }) & \gamma_m (X_{ub} - X_{um})\\
    L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (X_{ub} - X_{um})\\
    -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gamma_m (Y_{bm} - Y_{bb}) & \gamma_m (Y_{t } - Y_{bm}) & 0 & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gamma_t (Y_{t } - Y_{bm}) & \gamma_t (Y_{um} - Y_{t }) & 0\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gamma_m (Y_{um} - Y_{t }) & \gamma_m (Y_{ub} - Y_{um})\\
    -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gamma_b (Y_{ub} - Y_{um})\\
  \end{pmatrix}$%
  }
  \begin{pmatrix}
    \dot{\theta}_{bb}\\
    \dot{\theta}_{bm}\\
    \dot{\theta}_{um}\\
    \dot{\theta}_{ub}\\
    \lambda_{bs}\\
    \lambda_{bt}\\
    \lambda_{ut}\\
    \lambda_{us}\\
  \end{pmatrix}
  =
  \begin{pmatrix}
    -F_{bmx} + \gamma_m R_{bmx}\\
    -F_{tx} + \gamma_t R_{tx}\\
    -F_{umx} + \gamma_m R_{umx}\\
    -F_{ubx} + \gamma_b R_{ubx}\\
    -F_{bmy} + \gamma_m R_{bmy}\\
    -F_{ty} + \gamma_t R_{ty}\\
    -F_{umy} + \gamma_m R_{umy}\\
    -F_{uby} + \gamma_b R_{uby}\\
  \end{pmatrix}
  \]
}

This matrix is then solved using the Mathematica algebra system, resulting in a set of equations shown in Appendix (\ref{ob-motion-equations]}).

------------------------------------------

@@

\section{Chapter: Results}
	\subsection{Histograms}
		\subsubsection{Step length histograms}
		\subsubsection{Step time histograms}
	\subsection{Other ways to represent data?}

@@

\section{Appendix}

\subsection{Motion equations}

\subsubsection{Onebound equations}
\label{onebound-motion-equations}
These are the full motion equations used to time-evolve the onebound model:

\begin{align*}
AA &= L_s\sin\theta_{bb}      &   LL &= -L_s\cos(\theta_{bb})\\
BB &= L_t\sin(\theta_{bm})    &	 MM &= -L_t\cos(\theta_{bm})\\
CC &= -L_t\sin(\theta_{um})   &	 NN &= L_t\cos(\theta_{um})\\
DD &= -L_s\sin(\theta_{ub})   &	 OO &= L_s\cos(\theta_{ub})\\
\\
EE &= -\gamma_m (X_{bm} - X_{bb})       &  PP &= -\gamma_m (Y_{bm} - Y_{bb})\\
FF &= \gamma_m (X_{t } - X_{bm})        &	 QQ &= \gamma_m (Y_{t } - Y_{bm})\\ 
GG &= -\gamma_t (X_{t } - X_{bm})       &	 RR &= -\gamma_t (Y_{t } - Y_{bm})\\
HH &= \gamma_t (X_{um} - X_{t })        &	 SS &= \gamma_t (Y_{um} - Y_{t })\\ 
II &= -\gamma_m (X_{um} - X_{t })       &	 TT &= -\gamma_m (Y_{um} - Y_{t })\\
JJ &= \gamma_m (X_{ub} - X_{um})        &	 UU &= \gamma_m (Y_{ub} - Y_{um})\\ 
KK &= -\gamma_b (X_{ub} - X_{um})       &	 VV &= -\gamma_b (Y_{ub} - Y_{um})\\
\end{align*}%
%
\[
\begin{pmatrix}
  AA & 0 & 0 & 0 & EE & FF & 0 & 0\\
  AA & BB & 0 & 0 & 0 & GG & HH & 0\\
  AA & BB & CC & 0 & 0 & 0 & II & JJ\\
  AA & BB & CC & DD & 0 & 0 & 0 & KK\\
  LL & 0 & 0 & 0 & PP & QQ & 0 & 0\\
  LL & MM & 0 & 0 & 0 & RR & SS & 0\\
  LL & MM & NN & 0 & 0 & 0 & TT & UU\\
  LL & MM & NN & OO & 0 & 0 & 0 & VV\\
\end{pmatrix}
\begin{pmatrix}
    \dot{\theta}_{bb}\\
    \dot{\theta}_{bm}\\
    \dot{\theta}_{um}\\
    \dot{\theta}_{ub}\\
    \lambda_{bs}\\
    \lambda_{bt}\\
    \lambda_{ut}\\
    \lambda_{us}\\
  \end{pmatrix}
=
\begin{pmatrix}
  X1\\
  X2\\
  X3\\
  X4\\
  X5\\
  X6\\
  X7\\
  X8\\
\end{pmatrix}
\]

Solving the above system for $\dot{\Theta}_{bb}, \dot{\Theta}_{bb}, \dot{\Theta}_{bb}$ and $\dot{\Theta}_{bb}$ gives

\begin{multline}
d_bba = (-(GG*II*MM*NN*PP*X1) + CC*HH*MM*PP*RR*X1 -
      BB*HH*NN*PP*RR*X1 + BB*II*NN*PP*RR*X1 - CC*GG*MM*PP*SS*X1 +
      BB*GG*NN*PP*SS*X1 + CC*GG*MM*PP*TT*X1 - BB*CC*PP*RR*TT*X1 +
      FF*II*MM*NN*PP*X2 - EE*II*MM*NN*QQ*X2 + CC*FF*MM*PP*SS*X2 -
      BB*FF*NN*PP*SS*X2 - CC*EE*MM*QQ*SS*X2 + BB*EE*NN*QQ*SS*X2 -
      CC*FF*MM*PP*TT*X2 + CC*EE*MM*QQ*TT*X2 - FF*HH*MM*NN*PP*X3 +
      EE*HH*MM*NN*QQ*X3 + BB*FF*NN*PP*SS*X3 - BB*EE*NN*QQ*SS*X3 +
      EE*GG*II*MM*NN*X5 - CC*EE*HH*MM*RR*X5 + BB*EE*HH*NN*RR*X5 -
      BB*EE*II*NN*RR*X5 + CC*EE*GG*MM*SS*X5 - BB*EE*GG*NN*SS*X5 -
      CC*EE*GG*MM*TT*X5 + BB*CC*EE*RR*TT*X5 - CC*FF*HH*MM*PP*X6 +
      BB*FF*HH*NN*PP*X6 - BB*FF*II*NN*PP*X6 + CC*EE*HH*MM*QQ*X6 -
      BB*EE*HH*NN*QQ*X6 + BB*EE*II*NN*QQ*X6 + BB*CC*FF*PP*TT*X6 -
      BB*CC*EE*QQ*TT*X6 + CC*FF*HH*MM*PP*X7 - CC*EE*HH*MM*QQ*X7 -
      BB*CC*FF*PP*SS*X7 + BB*CC*EE*QQ*SS*X7)/ (EE*GG*II*LL*MM*NN +
      BB*FF*HH*LL*NN*PP - BB*FF*II*LL*NN*PP - AA*FF*HH*MM*NN*PP +
      AA*FF*II*MM*NN*PP - AA*GG*II*MM*NN*PP - BB*EE*HH*LL*NN*QQ +
      BB*EE*II*LL*NN*QQ + AA*EE*HH*MM*NN*QQ - AA*EE*II*MM*NN*QQ -
      CC*EE*HH*LL*MM*RR + BB*EE*HH*LL*NN*RR - BB*EE*II*LL*NN*RR +
      AA*CC*HH*MM*PP*RR - AA*BB*HH*NN*PP*RR + AA*BB*II*NN*PP*RR +
      CC*EE*GG*LL*MM*SS - BB*EE*GG*LL*NN*SS - BB*CC*FF*LL*PP*SS +
      AA*CC*FF*MM*PP*SS - AA*CC*GG*MM*PP*SS + AA*BB*GG*NN*PP*SS +
      BB*CC*EE*LL*QQ*SS - AA*CC*EE*MM*QQ*SS - CC*EE*GG*LL*MM*TT +
      BB*CC*FF*LL*PP*TT - AA*CC*FF*MM*PP*TT + AA*CC*GG*MM*PP*TT -
      BB*CC*EE*LL*QQ*TT + AA*CC*EE*MM*QQ*TT + BB*CC*EE*LL*RR*TT -
      AA*BB*CC*PP*RR*TT) - ((FF*PP - EE*QQ)*(HH*MM - BB*SS)*(JJ*NN -
      CC*UU)*(-(((Power(AA,6)*Power(BB,2)*CC*DD*HH*MM -
      Power(AA,6)*Power(BB,3)*DD*HH*NN +
      Power(AA,6)*Power(BB,3)*DD*II*NN -
      Power(AA,6)*Power(BB,3)*CC*II*OO)* (-(EE*LL) +
      AA*PP)*(-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) + AA*QQ)) + (-(EE*LL) +
      AA*PP)*(Power(AA,4)*BB*CC*GG*MM -
      Power(AA,2)*BB*CC*(-(AA*BB*FF*LL) + Power(AA,2)*FF*MM +
      Power(AA,2)*BB*RR))) - (-(EE*LL) +
      AA*PP)*((Power(AA,5)*Power(BB,3)*CC*DD*FF*LL -
      Power(AA,6)*Power(BB,2)*CC*DD*FF*MM +
      Power(AA,6)*Power(BB,2)*CC*DD*GG*MM -
      Power(AA,6)*Power(BB,3)*DD*GG*NN)* (-(EE*LL) + AA*PP) -
      (Power(AA,5)*Power(BB,3)*CC*DD*EE*LL -
      Power(AA,6)*Power(BB,2)*CC*DD*EE*MM)*(-(FF*LL) +
      AA*QQ))*(Power(AA,4)*BB*CC*HH*MM -
      Power(AA,4)*Power(BB,2)*CC*SS))*
      (-(((Power(AA,3)*Power(BB,2)*CC*FF*LL - Power(AA,4)*BB*CC*FF*MM
      + Power(AA,4)*BB*CC*GG*MM -
      Power(AA,4)*Power(BB,2)*GG*NN)*(-(EE*LL) + AA*PP) -
      (Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) + AA*QQ))*
      (-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(LL*X1) + AA*X5)) + (-(EE*LL) +
      AA*PP)*(Power(AA,3)*Power(BB,2)*CC*LL*X1 -
      Power(AA,4)*BB*CC*MM*X1 + Power(AA,4)*BB*CC*MM*X2 -
      Power(AA,4)*Power(BB,2)*CC*X6))) +
      (-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) + AA*QQ)) + (-(EE*LL) +
      AA*PP)*(Power(AA,4)*BB*CC*GG*MM -
      Power(AA,2)*BB*CC*(-(AA*BB*FF*LL) + Power(AA,2)*FF*MM +
      Power(AA,2)*BB*RR)))* (-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(LL*X1) + AA*X5)) + (-(EE*LL) +
      AA*PP)*(Power(AA,3)*Power(BB,2)*CC*LL*X1 -
      Power(AA,4)*BB*CC*MM*X1 + Power(AA,4)*BB*CC*MM*X2 -
      Power(AA,4)*Power(BB,2)*NN*X2 + Power(AA,4)*Power(BB,2)*NN*X3 -
      Power(AA,4)*Power(BB,2)*CC*X7)))) + (-((-(EE*LL) +
      AA*PP)*((Power(AA,3)*Power(BB,2)*CC*FF*LL -
      Power(AA,4)*BB*CC*FF*MM + Power(AA,4)*BB*CC*GG*MM -
      Power(AA,4)*Power(BB,2)*GG*NN)* (-(EE*LL) + AA*PP) -
      (Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) +
      AA*QQ))*(Power(AA,4)*BB*CC*HH*MM -
      Power(AA,4)*Power(BB,2)*CC*SS)) + (-(EE*LL) +
      AA*PP)*(-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) + AA*QQ)) + (-(EE*LL) +
      AA*PP)*(Power(AA,4)*BB*CC*GG*MM -
      Power(AA,2)*BB*CC*(-(AA*BB*FF*LL) + Power(AA,2)*FF*MM +
      Power(AA,2)*BB*RR)))* (Power(AA,4)*BB*CC*HH*MM -
      Power(AA,4)*Power(BB,2)*HH*NN + Power(AA,4)*Power(BB,2)*II*NN -
      Power(AA,4)*Power(BB,2)*CC*TT))*
      (-(((Power(AA,5)*Power(BB,3)*CC*DD*FF*LL -
      Power(AA,6)*Power(BB,2)*CC*DD*FF*MM +
      Power(AA,6)*Power(BB,2)*CC*DD*GG*MM -
      Power(AA,6)*Power(BB,3)*DD*GG*NN)*(-(EE*LL) + AA*PP) -
      (Power(AA,5)*Power(BB,3)*CC*DD*EE*LL -
      Power(AA,6)*Power(BB,2)*CC*DD*EE*MM)*(-(FF*LL) + AA*QQ))*
      (-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(LL*X1) + AA*X5)) + (-(EE*LL) +
      AA*PP)*(Power(AA,3)*Power(BB,2)*CC*LL*X1 -
      Power(AA,4)*BB*CC*MM*X1 + Power(AA,4)*BB*CC*MM*X2 -
      Power(AA,4)*Power(BB,2)*CC*X6))) +
      (-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) + AA*QQ)) + (-(EE*LL) +
      AA*PP)*(Power(AA,4)*BB*CC*GG*MM -
      Power(AA,2)*BB*CC*(-(AA*BB*FF*LL) + Power(AA,2)*FF*MM +
      Power(AA,2)*BB*RR)))* (-((Power(AA,5)*Power(BB,3)*CC*DD*EE*LL -
      Power(AA,6)*Power(BB,2)*CC*DD*EE*MM)*(-(LL*X1) + AA*X5)) +
      (-(EE*LL) + AA*PP)*(Power(AA,5)*Power(BB,3)*CC*DD*LL*X1 -
      Power(AA,6)*Power(BB,2)*CC*DD*MM*X1 +
      Power(AA,6)*Power(BB,2)*CC*DD*MM*X2 -
      Power(AA,6)*Power(BB,3)*DD*NN*X2 +
      Power(AA,6)*Power(BB,3)*DD*NN*X3 -
      Power(AA,6)*Power(BB,3)*CC*OO*X3 +
      Power(AA,6)*Power(BB,3)*CC*OO*X4 -
      Power(AA,6)*Power(BB,3)*CC*DD*X8)))))/ ((-(EE*GG*II*LL*MM*NN) -
      BB*FF*HH*LL*NN*PP + BB*FF*II*LL*NN*PP + AA*FF*HH*MM*NN*PP -
      AA*FF*II*MM*NN*PP + AA*GG*II*MM*NN*PP + BB*EE*HH*LL*NN*QQ -
      BB*EE*II*LL*NN*QQ - AA*EE*HH*MM*NN*QQ + AA*EE*II*MM*NN*QQ +
      CC*EE*HH*LL*MM*RR - BB*EE*HH*LL*NN*RR + BB*EE*II*LL*NN*RR -
      AA*CC*HH*MM*PP*RR + AA*BB*HH*NN*PP*RR - AA*BB*II*NN*PP*RR -
      CC*EE*GG*LL*MM*SS + BB*EE*GG*LL*NN*SS + BB*CC*FF*LL*PP*SS -
      AA*CC*FF*MM*PP*SS + AA*CC*GG*MM*PP*SS - AA*BB*GG*NN*PP*SS -
      BB*CC*EE*LL*QQ*SS + AA*CC*EE*MM*QQ*SS + CC*EE*GG*LL*MM*TT -
      BB*CC*FF*LL*PP*TT + AA*CC*FF*MM*PP*TT - AA*CC*GG*MM*PP*TT +
      BB*CC*EE*LL*QQ*TT - AA*CC*EE*MM*QQ*TT - BB*CC*EE*LL*RR*TT +
      AA*BB*CC*PP*RR*TT)* (-((-(EE*LL) +
      AA*PP)*(-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) + AA*QQ)) + (-(EE*LL) +
      AA*PP)*(Power(AA,4)*BB*CC*GG*MM -
      Power(AA,2)*BB*CC*(-(AA*BB*FF*LL) + Power(AA,2)*FF*MM +
      Power(AA,2)*BB*RR)))* ((Power(AA,6)*Power(BB,2)*CC*DD*HH*MM -
      Power(AA,6)*Power(BB,3)*DD*HH*NN +
      Power(AA,6)*Power(BB,3)*DD*II*NN -
      Power(AA,6)*Power(BB,3)*CC*II*OO)*(-(EE*LL) + AA*PP)*
      (-((Power(AA,3)*Power(BB,2)*CC*EE*LL -
      Power(AA,4)*BB*CC*EE*MM)*(-(FF*LL) + AA*QQ)) + (-(EE*LL) +
      AA*PP)*(Power(AA,4)*BB*CC*GG*MM -
      Power(AA,2)*BB*CC*(-(AA*BB*FF*LL) + Power(AA,2)*FF*MM +
      Power(AA,2)*BB*RR))) - (-(EE*LL) +
